\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-14 ase20/overview.tex
[ASE] Revised overview

In this section, we introduce the overall structure of \( \tool \)
depicted in Figure~\ref{fig:overview}.
Compared to the existing approaches shown in
Figure~\ref{fig:existing}, \( \tool \) automatically synthesizes
{\sf JavaScript Parser} and {\sf AST-\( \ires \) Translator} directly from
ECMAScript.

The motivation of automatically extracting syntax and semantics of JavaScript
from ECMAScript is twofold: 1) ECMAScript is written in a well-organized
style, and 2) it is available as HTML files using various HTML tags.
To easily manipulate ECMAScript written in HTML, we developed
{\sf Spec Extractor} in JavaScript to extract the syntax and semantics in JSON format.

>>>>

In this section, we introduce the overall structure of \( \tool \) depicted in
Figure~\ref{fig:overview}.  Compared to the existing approaches shown in
Figure~\ref{fig:existing}, our tool automatically synthesizes {\sf JavaScript
Parser} and {\sf AST-\( \ires \) Translator} directly from ECMAScript. The
motivation of this work is twofold: 1) ECMAScript is written in a well-organized
style, and 2) the writing style is converged since ES7 in 2016.

We explain how \( \tool \) utilize such common patterns in the writing style to
synthesize two modules with an example.  After {\sf Spec Extractor} extract
syntax and semantics in JSON format, our tool consists consists of two parts for
\textit{syntax} and \textit{semantics}.
